Time Series Bootstrapping For Solar Current

### 2021-12-15 deliverables/paper.Rmd
Introduction
I added an introduction to the paper and related our current output/peak hour bootstrapping to the total compensation of installing solar panels. A lot of articles online discussed whether or not it is worth it for a reader to install solar panels in their area. Figured we could use our output to determine whether it is worth it for Los Angeles residents.

TODO

>>>>

This project began with the search for a research paper
utilizing the process of Monte Carlo sampling or other 
statistcal computing methods. We landed on a few papers 
that did exatcly this, one titled, "SolarStat: Modeling 
Photovoltaic Sources through Stochastic Markov Processes". 
Instead of comparing our works of Monte Carlo simulations 
we were able to utilize a more recent topic discussed in class.
This of course was bootsrapping, a topic we didn't get too in
depth about; however, everything needed to know will be explained 
later on in the paper. Regarding our choice of articles, it was a
question of interest and importance. During the last decade the world
has seen a massive uptick in renewable energy pushes. With this 
new wave of renewables and the rather large misunderstanding of their
total power we decided it would be interesting to look into solar and 
what it was all about. The big question being asked regarding
solar power is whether or not it is worth heading the initial cost
of set up and general mantienance. Many websites inform users of 
just this, according to the Solar.com Learning Center, the average
solar panel net cost is $2,700 per 1.5 kilowatt-hour system (@solar.com). 
The biggest upside to solar panels is being able to slice down your 
energy bill, and eventually have it pay for itself. In order to 
calculate a solar panels net output experts recommend looking at three things. 
1. Determine your locations peak sun hours (average US around 4 hours/day)
2. Determine your energy compensation (average $0.03/kilowatt-hour (kWh))
3. Determine your solar panels net energy output
Once you have calculated these three numbers it is as easy as 
multiplying them together to receive your daily solar panel 
compensation (@energysage). As an example Energy Sage looked at 
California receiving 5 peak hours of sunlight a day with a single 
solar panel producing 290 watts/hour. Daily, this panel will produce 
around 1.5 kWh per day yielding the owner a rough compensation 
of $16.42 a year.

This paper looks at data from a 12 year period to determine the current 
output of a specified city. It can be used to determine 
on a month by month basis if a location produces a sufficient amount 
of current from a solar panel. Providing customers with an idea on 
whether or not they should make the investment that is solar.
